DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-01-05 2015CompleteDerivation/completeDerivation.tex
Formatting and reordering references

%\documentclass[aps,pra,10pt,twocolumn,floatfix,nofootinbib]{revtex4-1}
\documentclass[draft,smallextended,nospthms]{svjour3}

@@

However precise our measurements are, we can only gather a finite amount of statistics and each outcome is expressed by a finite set of digits; therefore, the set of outcomes is countable.\footnote{The information provided by the process as measured by Shannon's entropy\cite{Shannon} is finite.} Note that different outcomes for the same process can overlap. For example, $4.12 \pm 0.05$ cm and $4.13 \pm 0.05$ cm are both legitimate possible outputs of the same measurement device. But since all states must be distinguishable, given two arbitrary states there must be a process precise enough to tell them apart. That is, the potential outcomes associated with the two states do not overlap. For example, $4.12 \pm 0.0005$ cm and $4.13 \pm 0.0005$ cm do not overlap anymore.

@@

We recognize the equations as those for Hamiltonian mechanics on the extended phase space.\cite{Synge,Struckmeier}

@@

\begin{thebibliography}{0}

\bibitem{Shannon} Shannon, C. E., ``A mathematical theory of communication'', The Bell System Technical Journal, Vol. 27, pp. 379--423, 623--656, (1948).
\bibitem{Jaynes} Jaynes, E. T., ``Information theory and statistical mechanics'', Statistical Physics 3, pp. 181--218, (1963).
\bibitem{classical_dynamics} J. V. Jos\'{e}, E. J. Saletan, ``Classical Dynamics'', Cambridge University Press, (1998).
\bibitem{Gromov} Gromov, M. L., ``Pseudo holomorphic curves in symplectic manifolds'', Inventiones Mathematicae 82, pp. 307--347, (1985).
\bibitem{deGosson} de Gosson, M. A., ``The symplectic camel and the uncertainty principle: the tip of an iceberg?'', Foundations of Physics 39, pp. 194--214, (2009).
\bibitem{Stewart} Stewart, I., ``The symplectic camel'', Nature 329, pp. 17--18, (1987).
\bibitem{Lanczos} Lanczos, C., ``The variational principles of mechanics'', University of Toronto Press, (1949).
\bibitem{Synge} Synge, J. L.: Classical dynamics. Encyclopedia of Physics Vol 3/1, Springer (1960)

\bibitem{Struckmeier} Struckmeier, J., ``Hamiltonian dynamics on the symplectic extended phase space for autonomous and non-autonomous systems'', J. Phys. A: Math. Gen. 38, pp. 1257--1278, (2005).
\bibitem{Lee} Lee, J. M.: Introduction to Smooth Manifolds. Springer (2003)
\bibitem{LeeTM} Lee, J. M.: Introduction to Topological Manifolds. Springer (2000)
\bibitem{Lang} Lang, S. L.: Algebra. Springer (2002)
\bibitem{Young} Young, N.: An Introduction to Hilbert Space. Cambridge Univ. Press, Cambridge, UK (1988)

@@

\bibitem{Roland}  
 Thomas, R. E., Rosa, A. J.: The analysis and design of linear circuits. Wiley (2001)

@@

@@

>>>>

%\documentclass[aps,pra,10pt,twocolumn,floatfix,nofootinbib]{revtex4-1}
\documentclass[smallextended,nospthms]{svjour3}

@@

However precise our measurements are, we can only gather a finite amount of statistics and each outcome is expressed by a finite set of digits; therefore, the set of outcomes is countable.\footnote{The information provided by the process as measured by Shannon's entropy\cite{Shannon,Jaynes} is finite.} Note that different outcomes for the same process can overlap. For example, $4.12 \pm 0.05$ cm and $4.13 \pm 0.05$ cm are both legitimate possible outputs of the same measurement device. But since all states must be distinguishable, given two arbitrary states there must be a process precise enough to tell them apart. That is, the potential outcomes associated with the two states do not overlap. For example, $4.12 \pm 0.0005$ cm and $4.13 \pm 0.0005$ cm do not overlap anymore.

@@

We recognize the equations as those for Hamiltonian mechanics on the extended phase space.\cite{Synge,Lanczos,Struckmeier}

@@

\begin{thebibliography}{0}
\bibitem{Roland}  
Thomas, R. E., Rosa, A. J.: The analysis and design of linear circuits. Wiley (2001)

@@

@@

\bibitem{LeeTM} Lee, J. M.: Introduction to Topological Manifolds. Springer (2000)

\bibitem{Lee} Lee, J. M.: Introduction to Smooth Manifolds. Springer (2003)

\bibitem{Lang} Lang, S. L.: Algebra. Springer (2002)
\bibitem{Young} Young, N.: An Introduction to Hilbert Space. Cambridge Univ. Press, Cambridge, UK (1988)

\bibitem{classical_dynamics} Jos\'{e}, J. V., Saletan, E. J.: Classical Dynamics. Cambridge University Press, (1998)

\bibitem{Shannon} Shannon, C. E.: A mathematical theory of communication. The Bell System Technical Journal, Vol. 27, pp. 379--423, 623--656, (1948)

\bibitem{Jaynes} Jaynes, E. T.: Information theory and statistical mechanics. Statistical Physics 3, pp. 181--218, (1963)

\bibitem{Gromov} Gromov, M. L.: Pseudo holomorphic curves in symplectic manifolds. Inventiones Mathematicae 82, pp. 307--347, (1985)

\bibitem{deGosson} de Gosson, M. A.: The symplectic camel and the uncertainty principle: the tip of an iceberg?. Foundations of Physics 39, pp. 194--214, (2009)

\bibitem{Stewart} Stewart, I.: The symplectic camel, Nature 329, pp. 17--18, (1987)

@@

\bibitem{Synge} Synge, J. L.: Classical dynamics. Encyclopedia of Physics Vol 3/1, Springer (1960)

\bibitem{Lanczos} Lanczos, C.: The variational principles of mechanics, University of Toronto Press, (1949)

\bibitem{Struckmeier} Struckmeier, J.: Hamiltonian dynamics on the symplectic extended phase space for autonomous and non-autonomous systems. J. Phys. A: Math. Gen. 38, pp. 1257--1278, (2005)
